\chapter{Prerequisites}
\label{chap:02_prerequisites}

For the whistle sound source localization with multiple robots, some
sequential steps needs to interact for a final result.
To work with the implementations in \cref{chap:03_implementation}, the fundamentals
are introduced in this chapter on a general basis.

As this work specializes on the localization of a whistle sound, this sound pattern
must be detected at first.
This was already done by previous work \cite{Hasselbring}.
Hence, the flow of the whistle detection are briefly explained in \cref{sec:02_whistleSignal}.
The position of the sound source is determined by combining the
separate direction results on the single robots.
Utilizing the \ac{TDOA} information as in \cref{sec:02_tdoa} between the pairs
of the Naos' microphones, every robot produces a sound direction ray which
are feed into the team decision filter.
As mentioned in \cref{chap:01_introduction}, different methods exist to identify the \ac{TDOA}
and are terms of content in \cref{sec:02_cc,sec:02_gcc,sec:02_phase}.
Due to the low resolution arising from the sample rate and the distance between the microphones,
a subsample estimation is used based on \cref{sec:02_subsampleShift}.
One of the most significant factors is the selection of the signal frame that is used for
the direction determination.
In order to provide a correct and stable decision process, the different approaches to
consider are shortly mentioned in \cref{sec:02_signalStartDetection}.
After all, the results of the individual robots are filtered by assuming
gaussian distribution to produce a sound source position.
By passing information about the certainty of the single robot result, the
filtering explained in \cref{sec:02_filter} is related to a Kalman filter without
prediction step.

% \missing[]{
% - CC in time domain, because low frequency resolution (44100Hz/512samples=resolution)\\
% and also CC corrupted and we want to detect which signal was first\\
% }

\input{content/02_whistleSignal}
\input{content/02_TDOA}
\input{content/02_cc}
\input{content/02_gcc}
\input{content/02_phase}
\input{content/02_subsampleShift}
\input{content/02_startDetection}
\input{content/02_spectralSubtraction}
\input{content/02_teamFilter}
