\section{Multi-Agent Source Localization}
\label{sec:03_multiAgentLoca}

The final whistle-source localization is realized by collecting the
all \ac{WSDE} results of all active robots and combining the directions
into one xy-position outcome.
Two separate implementation details are covered in the following.
First, the actual localization algorithm that concludes the source localization
task is set in focus.
How the process of the multi-agent decision proceeds including the communication
is dealt with in \cref{subsec:03_teamCommunication}.
% -------------------------------------------------------------

As stated, the actual Bayesian updating filter algorithm is addressed first
by paying attention to \cref{alg:03_multiAgentLoca}.
With the specification of the filter made in \cref{subsec:02_2dTeam}, the
whistle-source localization is realized when the results of the individual robots
are available.
The multi-agent localization algorithm receives an array of rays that represent
the \ac{WSDE} results in the field coordinate system.
The whistle sound position to return consists of the x- and y-position $\vec{\mu}$ and
a covariance matrix \textbit{C}.
For each combination of the rays $R[j]$ and $R[k]$, the intersecting point position
$\vec{\mu}_{jk}$ along with its covariance matrix $\textbit{C}_{jk}$ is examined.
If such intersection exists, the whistle source position information is updated until all intersections are taken into consideration.

% PSEUDO CODE UPDATING ALGORITHM
\begin{algorithm}[H]
    \caption{Bayesian Updating}\label{alg:03_multiAgentLoca}
    \begin{algorithmic}[1]
        \Procedure {WhistleLocalization}{$array<R>$}
            \For{$j \in 0:R.size()$}
                \For{$k \in j+1:R.size()$}
                    \State $\vec{\mu}_{jk} \gets \Call{FindIntersection}{R[j], R[k]}$
                    \State $\textbf{\textit{C}}_{jk} \gets \Call{CalulateCovariance}{R[j], R[k]}$
                    \If{first intersection found}
                        \State $\vec{\mu} \gets \vec{\mu}_{jk}$
                        \State $\textbf{\textit{C}} \gets \textbf{\textit{C}}_{jk}$
                    \ElsIf{intersection found}
                        \State $\textbf{\textit{S}}_{jk} \gets \textbf{\textit{C}} + \textbf{\textit{C}}_{jk}$
                        \State $\textbf{\textit{K}}_{jk} \gets \textbf{\textit{C}} \cdot \textbf{\textit{S}}_{jk}^{-1}$
                        \State $\vec{\mu} \gets \vec{\mu} + \textbf{\textit{K}}_{jk} \cdot (\vec{\mu}_{jk} - \vec{\mu})$
                        \State $\textbf{\textit{C}} \gets \textbf{\textit{C}} - \textbf{\textit{K}}_{jk} \cdot \textbf{\textit{C}}$
                    \EndIf
                \EndFor
            \EndFor
            \State \textbf{return} $\vec{\mu}$
        \EndProcedure\vspace{12pt}
    \end{algorithmic}
\end{algorithm}
% -------------------------------------------------------------

\subsection{Team Communication}
\label{subsec:03_teamCommunication}

To agree on a whistle position as a multi-agent system by computing the whistle
localization algorithm \cref{alg:03_multiAgentLoca} \todo{das ist zwar so korrekt, liesst sich im PDF aber mega komisch durch "algorithm algorithm 1". Vielleicht nochmal den Satzbau aendern.}, the \ac{WSDE} results of the
stand-alone robots must be collected.
As introduced in \cref{sec:03_naoFramework}, the robots are able to send and receive
information from team mates wirelessly.
By present implementation, the team message includes a robot's xy-position information,
the orientation as well as the time point of the last detected whistle \todo{eher "among further information related to other tasks" oder so} (and much more).
Thus, only the angular \ac{WSDE} and its additional information like distance and \ac{PSNR}
are to be appended to the team message.

In order to wait for the team mates,
a delay of 3\si{\second} \todo{eher "three seconds"} is implemented before collecting the \ac{WSDE} results
of the other players.
By this artificially introduced delay, synchronization issues due to network lags and
whistle detection differences can be circumvented.
For each team mate available in the network, a ray object is created by considering the
last time when the whistle was heard, the robot position with its orientation and the \ac{WSDE} angle.
If the time point of the detected whistle differs more than 4\si{\second}, it is assumed that
the result does not involve the identical whistles and is not counted.

% \begin{algorithm}[H]
%     \caption{Team Data Collection}\label{alg:03_collectRays}
%     \begin{algorithmic}[1]
%         \Procedure {CollectPlayerData}{}
%             \For{$j \in 0:R.size()$}
%             \EndFor
%             \State \textbf{return} $array<R>$
%         \EndProcedure\vspace{12pt}
%     \end{algorithmic}
% \end{algorithm}
% % -------------------------------------------------------------