\chapter{Evaluation}

\change[]{Allgemeine Anmerkung: Ich finde es persoenlich bei diesen
Kapiteleinleitungen schoener, wenn die "section" immer am Anfang des satzes steht
damit man nicht vor und zurück springt. Aber das ist geschmackssache.}

In this chapter, experimental results are presented while setting
focus on different aspects.
Before evaluating the performance of the final localization algorithm the
\ac{WSDE} on single robots is examined by first taking a closer look
at a representative example in \cref{sec:04_tdoaSingle}.
There, the focus is set on the \ac{TDOA} methods itself for each channel pair
before combining them to a robot direction result.
\Cref{subsec:04_singleRobotAngleError} presents the validity of the methods with
regard to a whole set of data.

% Additional Info
In \cref{chap:03_implementation}, the presence of additional
information next to the estimated \ac{WSDE} on individual robots
is discussed.
This includes knowledge about \acp{SNR} of the channel signals, the \ac{PSNR}
of the \ac{GCC} functions and a distance approximation if the signal source
is detected straight in front or from behind.
\Cref{sec:04_additionalInformation} analyses if and to
what extent these factors are useful for the \ac{WSDE} or \ac{WSL}.

% Team filter
To examine the whistle sound source localization of the robots as team,
measurements were taken with five Naos on the field of the HULKs' laboratory
as specified in \cref{subsec:04_labMeasurements}.
In \cref{sec:04_multiAgentLoca} the performance of the \ac{TDOA} methods are presented
and compared for all measurements.
Depending on the accuracy of the individual direction results, the quality
of the team filter is limited.
% Therefore, the angular error of the single robots is demonstrated for each
% measurement and method.

All measurements presented in this chapter were recorded in the
laboratory of the HULKs and are taken from a sound source at a height of
\SI{1.5}{\meter} above ground.
The size of the field used in this work is smaller than the regular \ac{SPL}
field with 7.5\si{m} length and 5\si{m} width instead of 9\si{\meter} and 6\si{\meter}.
This circumstances occur due to lack of space and limited size of the
field room in the laboratory.
Another deviation to competition conditions arise due to walls being next to field borders.
In \cref{subsec:04_labMeasurements} further information about the measurement setup
is introduced.

\input{content/04_measurements}
\input{content/04_signalStartDetection}
\input{content/04_tdoa}
\input{content/04_additionalInfo}
\input{content/04_teamDecision}

\todo[inline]{General, use pont instead of comma for numerical values}